\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 metatheory-condensed.tex
no longer mentioning structural typing

\TT is intended as a foundational model. So unlike our programmer-facing plugin,
typing is structural rather than nominal\EDJ{I don't actually know what do you mean by structural here. I think surface syntax (Coq) is pretty structual as well.}, and
fields automatically axiomatized by the plugin require explicit definitions in \TT.
%
\TT provides MLTT-style constructs that can be used to express families and
family polymorphism. %rather than building it in directly.
%
Most notably, it extends MLTT with what we call \emph{linkages}.
(Linkages are a namesake of the theoretical device through which prior work~\cite{zm2017} models
family polymorphism in an OO setting, but the technical details differ significantly from the prior work.)

\begin{itemize}
[labelsep=*,leftmargin=1pc,itemsep=3pt]
\item 
Linkages model families, so they are like tuples composed of the fields.
But there is a twist: they support late binding.
Unlike dependent tuples where a later component is \emph{existentially}
quantified over the earlier ones, a linkage component is \emph{universally}
quantified over---and thus polymorphic to---components preceding it.

>>>>

\TT is intended as a foundational model. So unlike our programmer-facing plugin,
%typing is structural rather than nominal\EDJ{I don't actually know what do you mean by structural here. I think surface syntax (Coq) is pretty structual as well.}, and
fields automatically axiomatized by the plugin require explicit definitions in \TT.
%
\TT provides MLTT-style constructs that can be used to express families and
family polymorphism. %rather than building it in directly.
%
Most notably, it extends MLTT with what we call \emph{linkages}.
(Linkages are a namesake of the theoretical device through which prior work~\cite{zm2017} models
family polymorphism in an OO setting, but the technical details differ significantly from the prior work.)

\begin{itemize}
[labelsep=*,leftmargin=1pc,itemsep=3pt]
\item 
Linkages model families; they are like tuples composed of the fields,
with field names represented by variable bindings.
But there is a twist: linkages support late binding.
Unlike dependent tuples where a later component is \emph{existentially}
quantified over the earlier ones, a linkage component is \emph{universally}
quantified over---and thus polymorphic to---components preceding it.
